---
title: "Derivatives in R - Handout"
author: "Ruth Enriquez"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
```

#Find the derivative expression and slope at the indicated value a. $$f(x)=x^2, x = 3$$

```{r}
ex_1 <-expression(x^2)

my_derivative <-deriv(ex_1, "x")
my_derivative

#find the slope

x <-3
eval(my_derivative)
```

b.  $$P(a)=2(3a+2)^4-5, a =1.5$$

```{r}
ex_2 <- expression(2 * (3*a + 2)^4+5)

my_derivative_2 <-deriv(ex_2,"a")

a <-1.2
eval(my_derivative_2)
```

c.$$g(t)=-4t/(t^2+1)^3, t=0$$

```{r}
ex_3 <- expression(-4*t/(t^2+1)^3)

my_derivative_3 <-deriv(ex_3,"t")

t <-0
eval(my_derivative_3)
```

#Make a Penguin Plot to view table of data write, view(penguins), you just need the dataset not the whole name

#Create a ggplot

```{r}
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm)) + 
  geom_point(aes(color = species)) +
  theme_minimal()+
  labs(x = "Bill Length (mm)",
      y = "Bill Depth (mm)", title = "Comparing Penguin Bill Length and Depth" )
```

#Create a jitterplot of flipper length by species x axis - species y axis - flipper length
#to update graph into a jitterplot, ADD geom_jitter to you ggplot
#x - axis: species
#y - axis: flipper length

```{r}
ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) + 
  geom_jitter(aes(color = species),width = .2) +
  theme_minimal()+
  labs(x = " Species",
      y = "Flipper Length (mm)", title = "Penguin Flipper Length Analysis" )
```
